An Open Platform for Managing Short Programming Exercises

### 2013-06-20 paper/paper.tex
incentives

{\bf If exercises are shared freely, is the availability of solutions a concern?}
Discuss.

{\bf Should exercises be graded?}
Discuss.

{\bf What are the appropriate incentives to encourage students to attempt
the exercises (and get the maximum benefit from them)?}
Discuss.

>>>>

{\bf Should exercises be graded?
If exercises are shared freely, is the availability of solutions a concern?}
These questions are related: if exercises are available publicly,
solutions will likely be available publicly as well.  (For example,
many if not all CodingBat problems have solutions which can be found
through a web search.)  If exercises are graded, then some students may
choose to cheat rather than attempt to solve the problem honestly.

{\bf What are appropriate incentives to encourage students to attempt
the exercises (and get the maximum benefit from them)?}
If exercises are not graded, then what incentives can be used to
encourage students to make a serious attempt at solving them?
